Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-06-10 ms.qmd
Small update
Re-render

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, performance, ggthemes)

@@

We also extracted climate projections into the future to understand the effects of climate warming will have on opportunity for selection. We used the CanESM2 climate model (2096-2100) under a high emissions scenerio (RCP8.5).

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage, gt, performance, ggthemes, mapproj)

@@

We also extracted climate projections into the future to understand the effects of climate warming will have on opportunity for selection. We used the CanESM2 climate model (2005-2100) under a high emissions scenerio (RCP8.5).
